Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-02-25 rebuttal/rebuttal_response_max_500_words.txt

We thank the reviewers for their comments. We summarize and respond to them in what follows.

[Reviewer 1] ICDAR Contest in 2011 related to that topic
Thanks for pointing this out. They are essentially using a full-cross evaluation of all methods to perform end-to-end evaluation, just like us. Also, they do not report NER evaluation, unlike us.
[TODO add ref to https://hal.archives-ouvertes.fr/inria-00608371 + small comment]  We updated the paper with these precisions.

[Reviewer 1] Qualitative analysis of influence of OCR quality on NER
[Reviewer 1] Metrics uses, potential biases

[Bertrand] Ajouter un paragraphe d'évaluation qualitative des résultats de l'ocr+ner comme on avait prévu initialement, et un commentaire la projection des labels dans les chaînes bruitée. 
[Joseph] say we used metrics as reported on previous work, and also that one of our goals is to assess whether NER could help correcting OCR errors?
Here OCR is either pretty good or very wrong, so alignments usually make sense or can be detected as degenerated cases. However, it is very true that some borderline cases may cause trouble. This requires more study and [TODO] we updated the paper to be more explicit about these limitations.

[Reviewer 2] comparing two runs of Pero OCR together, or two runs of Tesseract together
Very good point, but we could not compete with the large, private training datasets used to produce the models we used. We chose to report, as objectively as possible, the performance of actual, off-the-shelf systems.

[Reviewer 2] reason for not reporting Kraken performance on downstream NER
[Bertrand] Ajouter Kraken à l'évaluation NER ? 
(say we chose not to report this because would have reduced a lot the size of the test set? This would require to add one extra set of experiment; not possible because of space constraints)

[Reviewer 2] missing Figure 1 reference, inconsistent reference to figures, Tesseract spelling
Thanks for pointing these issues, [TODO] we fixed them.

[Reviewer 2] Experiment with artificial OCR noise in future work
This is planned, but it seems to be very hard to generate realistic noise.
We decided to first focus on real cases with no further assumptions.

[Reviewer 3] Section 2.3 should be a separate section about the pipeline
[RBertrand] Transformer la sous-section 2.3 "Pipeline summary" en section 3. 
[TODO attention espace supplémentaire] We extracted this content as a new section as suggested.

[Reviewer 3] What are "thumbnails" in page 7
We refer to "thumbnails" as image crops, have the same resolution as the original image.
We updated the text to clarify this.

[Reviewer 3] Description of NER QA is confusing
[TODO] we clarified the relevant section

[Reviewer 3] Figure 4 needs clarification
[Bertrand] Détailler la légende de la figure 4 ? 
[TODO] We improved the description of fig. 4.

### 2022-02-27 rebuttal/rebuttal_response_max_500_words.txt

We thank the reviewers for their comments. We summarize and respond to them in what follows.

[Reviewer 1] ICDAR Contest in 2011 related to that topic
Thanks for pointing this out. They are essentially using a full-cross evaluation of all methods to perform end-to-end evaluation, just like us. Also, they do not report NER evaluation, unlike us.
[TODO add ref to https://hal.archives-ouvertes.fr/inria-00608371 + small comment]  We updated the paper with these precisions.

[Reviewer 1] Qualitative analysis of influence of OCR quality on NER
[Bertrand] say that effects of OCR noise are indeed non-uniform on NER results. The impact on structuring elements of the entries like punctuation symbols appears to be most significant, as they mark the separation between semantically homogeneous blocks (e.g. between PERS and ACT). We plan to carry out a more in-depth qualitative study in the near future ?

[Reviewer 1] Metrics uses, potential biases
[Bertrand] Ajouter un paragraphe d'évaluation qualitative des résultats de l'ocr+ner comme on avait prévu initialement, et un commentaire la projection des labels dans les chaînes bruitée. 
[Joseph] say we used metrics as reported on previous work, and also that one of our goals is to assess whether NER could help correcting OCR errors?
Here OCR is either pretty good or very wrong, so alignments usually make sense or can be detected as degenerated cases. However, it is very true that some borderline cases may cause trouble. This requires more study and [TODO] we updated the paper to be more explicit about these limitations.

@@

[Reviewer 2] comparing two runs of Pero OCR together, or two runs of Tesseract together
Very good point, but we could not compete with the large, private training datasets used to produce the models we used. We chose to report, as objectively as possible, the performance of actual, off-the-shelf systems.

[Reviewer 2] reason for not reporting Kraken performance on downstream NER
We chose not to report Kraken performances as it would have drastically reduced the size of the labelled sets "NER-x" and thus hampered the other evaluations on the reference, pero and tesseract datasets.
All labelled datasets contains the same subset of directories entries by construction (section 3). Kraken performs quite poorly, which hinders the projection of labels from the ground truth and drastically reduces the size of the subset of labelled entries.

[Reviewer 2] missing Figure 1 reference, inconsistent reference to figures, Tesseract spelling
Thanks for pointing these issues, [TODO] we fixed them.
(Refs. to figures fixed)
(About T/tesseract : is he refering to fig 7 ? If so, "tesseract" is the name of the test set from "NER-tesseract").

[Reviewer 2] Experiment with artificial OCR noise in future work
We plan to perform such experiments following e.g. the techniques presented in https://doi.org/10.1007/978-3-030-86331-9_48
As it seems to be quite hard to generate realistic noise, we decided to first focus on real cases with no further assumptions.

[Reviewer 3] Section 2.3 should be a separate section about the pipeline
[TODO attention espace supplémentaire] We extracted this content as a new section as suggested.

[Reviewer 3] What are "thumbnails" in page 7
We refer to "thumbnails" as image crops, have the same resolution as the original image.
We updated the text to clarify this. (TODO ?)

### 2022-02-28 src-latex/parts/30-dataset.tex
wip rebuttal
Add section 3

% !TeX root = ../main-paper.tex
\section{Dataset}
\label{sec:dataset}

% Conventions nommage
% Dataset annoté à la main = "ground truth"
% ground truth aligné = "ner-reference"
% entrées pero aligné = "ner-pero"
% entrées tesseract alignées = "ner-tesseract"

%In this work, we  aim  at  producing  structured  spatio-temporal  data  from the information contained in the XIX\textsuperscript{th} century Parisian trade directories.
%To do this, it is therefore necessary to extract the text from the scans of the directories to be processed and to identify the entries in the various indexing lists used.
%Then, in each of these entries, the named entities they contain have to be extracted to produce structured spatio-temporal data representing the evolution over time of the people and businesses listed in these directories, their descriptions and their locations.
%Both of these extraction tasks require data to train and evaluate the OCR and NER approaches identified as potentially relevant: Tesseract and PERO OCR for the OCR task and Spacy and CamemBERT - pre-trained or fine-tuned - neural models for the NER task.

This section presents the historical sources that we selected and their contents. It also details the construction of the groundtruth dataset leveraged in our experiments and the metrics used to evaluate OCR and NER results.

\subsection{A selection of Paris trade directories from 1798 to 1854}
\label{sec:corpus}

The directories are available from different libraries in Paris and have been digitised independently in various levels of quality. 
They cover a large period of time and originate from several publishers.
Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}).
We want our groundtruth dataset to be representative of the diversity of directories available in the period.

\begin{figure}[htb!]
	   \center{\includegraphics[width=0.9\textwidth]
	       {./images/DirectoryExcerpts2.png}}
	  \caption{\label{fig:directories} Examples of directory layouts and contents: 1) Duverneuil et La Tynna 1806 - index by name; 2) Deflandre 1828 - index by activity ; 3) Bottin 1851 - index by street name}
\end{figure}

Directories contain lists of people with various information attached.
For instance, the directory published by \emph{Didot} in 1854 contains three redundant lists of people sorted by name, by activity and by street name.
A typical example entry from this directory is ``\textit{Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47.}''.
It begins with the person's name and surname, here inside parentheses.
The glyph denotes that this person was awarded the \textit{Légion d'Honneur}.
Then comes a description of the person's activity, here his profession (professor at the Conservatory of music and declamation), but it can also be a social status.
Such descriptions range from a single word to paragraphs describing the occupation in full detail.
The street name and number where the person lives or carries out their activities ends the entry.

These are the pieces of information that we want to extract, deduplicate  and structure to build a spatio-temporal database.
Except for some potentially wordy activity descriptions, they correspond to named entities. However, while most entries contain the same types of named entities, their order and the way they are written vary from one directory/index to another. To provide examples of each entry structure, pages from each type have thus been annotated. %\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

\subsection{A dataset for OCR and NER evaluation}

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/protocol.pdf}
    \caption{Data extraction pipeline with two quality control checkpoints. The
    NER Q.A. checkpoint may either assess the NER system lonely (the dashed
    \emph{groundtruth} path) or may evaluate the joint work of a NER
    system with an OCR system.}
    \label{fig.pipeline}
\end{figure}

The simplified data extraction pipeline depicted in~\cref{fig.pipeline} processes the documents presented
in~\cref{sec:corpus}. First, the page layout extraction and entry segmentation are performed with a
semi-automated system and checked by a human. The resulting images, representing 8765 entries, are the inputs of a customizable two-stage pipeline.

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. An OCR system runs
on the thumbnails of each segmented entry to extract its text. An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). 
Some glyphs used in this dataset might be unknown to the OCR, and some like
\scalerel*{\includegraphics{./images/LH.png}}{H} do not even have a Unicode codepoint, and were annotated using Unicode Private User Area 1.
Furthermore, as some annotations guidelines where unclear to human annotators, some projections rules were applied: whitespace, dash, dots and a couple of commonly confused characters where projected to well-defined codepoints.
The same normalization was applied to OCR predictions.
At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed on the basis of the $8,765$ entries which were manually controlled, totalling $424,764$ characters (including $54,387$ spacing characters). Entries are $49.0$-characters long on average.

%2. Entrée/Sortie
\textbf{NER Stage.} The second stage of the pipeline aims at extracting the named entities from a text with a NER
system. This text originates from the OCR outputs in a real-word scenario but might be the groundtruth text in order to
evaluate the NER performance independently. There are 5 types of entity to detect~(see.~\cref{tab.entities}).
The NER system has to classify non-overlapping parts of the text into one of these entities (or none of them). A second
Q.A. (namely, NER Q.A.) is performed at the end of this stage between the groundtruth and the NER output.

Note that the dataset used to assess the NER stage is a subset of the entries. Indeed, we need to ensure that the datasets
contain the same entries whichever the OCR used in the previous stage. Entries where the OCR produced an empty string
and those for which no entity could be projected from the groundtruth have to be ignored. 
We filter the set of entries by keeping only the entries that are always valid at the end of the stage 1.
%At the cost of losing 5\% of the references entries, we thus have 8341 valid entries at the input of the stage 2.
% /!\ True only for \peroocr and Tesseract predictions, not considering Kraken (we loose 500 more entries)
Therefore, the $8,765$ reference entries were manually annotated with $34,242$ entities; entries contain $3.9$ entities on average.
Projecting reference tagged entities on OCR predictions resulted in a variable loss of entries.
For \peroocr, $8,392$ valid entries were generated, for Tesseract $8,700$ and for Kraken $7,990$.
The resulting intersection of the sets of valid entries contained $7,725$ entries for the tree OCR systems (and the reference),
or $8,341$ entries if we consider \peroocr and Tesseract only.

\begin{table}
\caption{Entities to recognise in the dataset.}
\label{tab.entities}
\small
\begin{tabular}{llp{8cm}}
Entity & Count & Description\\    
PER & 8788 & a person name or a business name, usually referred to as several person names. First names, initials, or civility mentions are included. E.g.: \textit{Alibert (Prosper)}, \textit{Allamand frères et Hersent},\textit{Heurtemotte (Vve)}. \\
TITLE & 483 & an honorary title, either text, glyphs or a combination of the two. E.g: O. \scalerel*{\includegraphics{./images/LH.png}} {H} for \textit{Officier de la Légion d'Honneur} or \scalerel*{\includegraphics{./images/GMLondon.png}}{H} for the Great Medal at the London exhibition.\\
ACT & 6472 & the profession or social status of a person summarised in the single concept of activity. E.g.: \textit{horlogerie}, \textit{export en tous genres}, \textit{Conseiller d'État}, \textit{propriétaire}.\\
LOC & 9709 & mostly street names (\textit{r. de la Jussienne}), but may also be neighbourhoods (\textit{Marais du Temple}) or any indirect spatial references (\textit{au Palais Royal}).\\
CARDINAL & 8747 & a street number, as part of an address (16, 5 bis), or a range of numbers (e.g. 23-25 or 5 \textit{à} 9).\\
FT & 43 & a geographic entity type, used to give more details on a location, e.g. \textit{boutique}, \textit{atelier}, \textit{fab.} or \textit{dépôt}. \\
\end{tabular}
\end{table}

%
%TODO average number of tags/entities per entry
%TODO lists actual dataset content: set of entries. For each entry:
%\begin{itemize*}
%    \item ref to original book, page, region
%    \item human transcription (OCR GT)
%    \item human NER (NER GT)
%    \item [GENERATED] OCR produced by Pero OCR, Tesseract v4, Kraken (precise model used)
%    \item [GENERATED] NER GT aligned on text predictions from Pero OCR, Tesseract v4, Kraken
%\end{itemize*}

>>>>

% !TeX root = ../main-paper.tex

\section{A two-stage pipeline to assess OCR and NER performances on historical texts}
\label{sec:pipeline-summary}

\begin{figure}[h!]
    \includegraphics[width=\linewidth]{figs/protocol.pdf}
    \caption{Data extraction pipeline with two quality control checkpoints. The
    NER Q.A. checkpoint may either assess the NER system lonely (the dashed
    \emph{groundtruth} path) or may evaluate the joint work of a NER
    system with an OCR system.}
    \label{fig.pipeline}
\end{figure}

The proposed pipeline to evaluate the extraction and annotation of historical directories is depicted in~\cref{fig.pipeline}
First, the page layout extraction and entry segmentation are performed with a
semi-automated system and checked by a human.
The resulting images are the inputs of a customizable two-stage pipeline detailed in this section.

\subsection{OCR and NER systems considered}
\label{subsec:ocr-ner-tools}
We chose to test three OCR systems: Tesseract, \peroocr, and Kraken. 
We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
In \cref{sec:dataset}, we will explain the evaluation protocol used to assess the combined performance of these OCR and NER systems.

\textbf{Tesseract} is a long-living project, born as a closed-sourced OCR at Hewlett-Packard in the eighties, it was progressively modernized, then open-sourced in 2005. From 2006 until November 2018, it was developed by Google and is still very active. We used in our tests version 4.1.1, released Dec. 26, 2019. Version 5, released on Nov. 30, 2021, has not been integrated in our tests yet.

\textbf{Kraken} is a project created by Benjamin Kiessling several years ago (development can be traced back to 2015), and is actively used in the open-source eScriptorium project \cite{kiessling_escriptorium_2019}.
As no pre-trained model for modern French was easily available, we used the default English text recognition model trained on modern printed English by Benjamin Kiessling on 2019. Models can be easily found and downloaded thanks to their hosting on Zenodo.

\textbf{\peroocr} is a very recent project (started in 2020) from the Brno University of Technology in Czech Republic.
Their authors used many state-of-the-art techniques to train it very efficiently.
We used the version from the master branch of their GitHub repository, updated on Sep 15, 2021.
We used the pre-trained weights provided by the authors on the same repository, created on Oct. 9, 2020 from European texts with Latin, Greek, and Cyrillic scripts.
% https://github.com/DCGM/pero-ocr
% https://www.fit.vut.cz/~ihradis/pero/pero_eu_cz_print_newspapers_2020-10-09.tar.gz

\textbf{SpaCy} is a software library that offers NLP components assembled in modular pipelines specialised by language.
Although BERT is available in the latest version of SpaCy (v3), the pipeline for French does not provide a NER layer at the time of our experiments (as of January 2022).
Hence, we rely on SpaCy's ad hoc pipeline trained on French corpora and capable of Named Entity Recognition.
% deep-sequoia and wikiner-fr, capable of named entity recognition.\textit{fr\_core\_news\_lg}\footnote{https://spacy.io/models/fr} trained two corpora in French: deep-sequoia and wikiner-fr, capable of named entity recognition.
The global architecture of these pipelines have not been yet published but are explained by the developers on their website.
Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics.
The classification layer relies on a finite-state machine whose transition probabilities are learnt using a multi-layer perceptron.
% \bertrand{Drop the next sentences if we need space}
% In 2018~\cite{won2018} evaluated SpaCy's NER ability to detect place names in five corpora of ancient letters written in English.
% They measured an average F1 score of 0.57.
% The SpaCy developers claim an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.
%For our experiments, the French model \textit{fr\_core\_news\_lg} is fine-tuned using our ground truth corpus.

\textbf{CamemBERT} is well-known adaptation of the BERT transformer-based model for the French language\cite{vaswani2017attention,devlin2018bert,martin-etal-2020-camembert}. Such language models have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer, usually referred as a "head". 
They can also be pre-trained in an unsupervised way on large amount of unlabeled texts for domain adaptation.
